Molecular dynamics simulation of a driven synchronized particle

### 2021-03-30 manuscript/manuscript_ajp_version2.tex
cleaned up exercises

\section{Introduction} 
Synchronization is a universal phenomena
in which
individual oscillators change frequency due
to external stimuli.\cite{Pikovsky2003}
The
flickering patterns of
candle flames %[DM - the air molecules are oscillating I think xx is a flame an oscillator? xx]
mediated by temperature fluctuations,\cite{Okamoto2016}
the vibrations of singing wine glasses interacting 
through sound waves,\cite{Arane2009}
and metronomes vibrating through a supporting platform\cite{Jia2015}
are examples of in-phase coupled oscillations. 
Biological systems benefit from cooperative
synchronization --
birds coordinate wing flaps
to optimize energy use during flight,\cite{Portugal2014}
frogs alternate croaking patterns,\cite{Aihara2014}
humans clap in time with music,\cite{Tranchant2016}
and 
at a cellular level, 
neurons simultaneously fire in cardiac muscle\cite{MartinHall1999}
and brain tissue.\cite{Singer1999}
External forcing can cause or regulate 
synchronization. For example, 
an electrical pacemaker 
regulates a heart beat 
and 
a pulsed light modifies the
flashing pattern of fireflies.

@@

In Sec.~\ref{sec:conclusion}
we describe how our results apply 
to physical systems,
such as optically trapped colloids
%charge density waves in dusty plasma
%[DM rewrote to better align with conclusion xx added words is this correct? xx]
and superconducting vortices in the presence of periodic pinning arrays.
% and Josephson junctions. %[DM resolved xx Josephson junctions not explicitly mentioned in conclusion, xx] 
We include problems for interested readers 
in Sec.~\ref{sec:problems}.

\section{Simulation}
\label{sec:MD}
We use a classical model for 
studying the dynamics, %xx you only use single particles xx]
using the net force on a particle to calculate
its trajectory.
The particle is confined in a two-dimensional (2D) %[DM singlular]
simulation of area $A = L \times L$, where $L=46.\bar{6}\,a_0$
where $a_0$ is a dimensionless unit of length.
%[DM - yes.  in the simulation we just use L=46.6 and the a_0 is to satisfy readers unfamiliar with simulation units xx confused about the role of $a_0$ because it and hence $L$ are dimensionless, Is it really the size of a colloid particle, which in the simulation you set to unity?  xx]
The particle %Particle $i$ %[DM resolved xx since we are doing non-interacting particles and thus only one particle is moving can we eliminate the subscript $i$? xx]
has
position $\vec{r} = x \hat{x} + y \hat{y}$
and velocity $\vec{v} = d\vec{r}/dt$.
The edges of the system are treated by
periodic boundary conditions,
such that a particle leaving the edge of the system is mapped
back to a position within the simulation boundaries 
by the transformation $x+L \rightarrow x$ and $y+L \rightarrow y$.
We show a schematic of the system in Fig.~\ref{fig:1_landscape}(a).
The units of the simulated variables are summarized in Table~\ref{tab:1}.
%\footnote{To learn more about the effects of temperature on this simulation see Problem~\ref{ex:brownian}, where we study $U_0 \sim k_B T$.}

We confine the particles using a position dependent 
potential energy, called a landscape or substrate.
The landscape is modulated in the $y$-direction
by the periodic function 
 \begin{equation}
   U(y) = U_0 \cos{(2 \pi y / \lambda)},
     \label{eq:ysubstrate}
\end{equation}
where $\lambda=L/N_p$, with $N_p$ equal to the number of periods,
and $U_0$ is a parameter
 that sets the depth of the minima
 with simulation units of energy $E_0$. 
 We plot this function in 
 Fig.~\ref{fig:1_landscape}
 for $N_p = 3$.  In Fig.~\ref{fig:1_landscape}(a) we show 
 the $x$-$y$ plane with a contour plot of $U(y)$ 
 to illustrate
 the 2D potential energy landscape;
 the maxima are colored gray and the minima colored white.
 %[DM - switch from red/blue to white/gray - xx make sure that all your figures make sense when printed in b/w xx]

The confining force on the particle %[DM removed subscripts] $i$
 is given by
 \begin{equation}
 \vec{F}_{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}). %DM removed ^{\ell}
 \label{eq:dudr}
 \end{equation}
 %[xx what does the superscript $\ell$ mean? xx]
 where $\ell$ denotes the landscape.
 In Fig.~\ref{fig:1_landscape}(b) we plot  
 $U(y)$ to illustrate how the magnitude
 $|\vec{F}_{\ell}|$ is calculated from the particle position $y$.
 %[DM - begrudingly changed - My collaborators and I consistently use superscripts for these equations to separate the force superscripts from the particle index subscripts.  This is consistent with the textbook I teach from.  xx suggest that you use subscripts instead of superscripts. We can easily make that change in the next iteration of your manuscript. However, you would need to change the figures, e.g., $\vec{F}_{\rm d}$ $F_{\rm dc}$ $F_{\rm ac}$. One of us didn't like superscripts where he was an undergraduate!  xx]

@@

The equation of motion provides a direct calculation of the velocity
of an individual particle at position $\vec{r}$ 
and simulation time $t$.
The   simulation is controlled by a  loop
which runs to a maximum integer time step.
At each time step
we evaluate the net force on each particle as a function of its position
$\vec{r}(t)$
and then integrate
the equation of motion to move particles
to an updated position.
Because the acceleration is zero,
the integration of the equation of motion
is performed via 
the simple first-order Euler method 
\begin{equation}
  \vec{r}(t+\Delta t) = \vec{v}(t) \Delta t + \vec{r}(t)
    \label{eq:euler}
\end{equation}
for a time step $\Delta t = 0.1\,\tau$.
In 
Problem~\ref{ex:euler}
we describe 
the numerical methods for 
solving differential equations.
%------------------------------------------------------------------
\begin{figure} % [h!]
\centering
\includegraphics[width=\columnwidth]{fig1_landscape.pdf}
\caption{
Schematic of the simulation of a single particle
  driven across a washboard potential energy landscape.
  (a) View of the $x$-$y$ plane. 
  The time-dependent applied driving force $\vec{F}_{\rm d}$
  is parallel to the $y$-axis.
  The landscape is shown with
  %[DM changed color scheme from red/blue to gray/white for better BW conversion]
  maxima in the potential energy are gray %#red
  and minima are white %.
  A particle is 
  subject to competing forces of the landscape and applied driving force.
  (b) The potential energy function
  along the $y$-axis $U(y)$.  %DM removed _{\ell}
  The particle in (a) is shown at the same $y$-position.
  The slope of $U(y)$ %[DM removed _{\ell} use the subscripts with the potential, but will move to superscript xx used subscript here xx]
  is the 
  magnitude of force $\vec{F}_{\ell}$. 
  }
\label{fig:1_landscape}
\end{figure}
%
\section{Mode-locking of a single particle}
% In subsection headings, only the first word is capitalized.
\label{sec:results}
Here we drive 
a single particle 
across the landscape. 
The numerical implementation of the landscape 
is calculated with Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  %[DM - right, two negative signs, one from the derivative, the other from the definition of force.  I found the ``mistaken'' dropped minus sign in the depths of january and added it.  xx but you should get a + sign not a minus sign xx] 
\begin{equation}
  \label{eq:force}
  {F_{\ell}}_y(y) = A_{p} \sin{(2 \pi y / \lambda)},
\end{equation}
where the force is scaled by the parameter $A_{p} = 2\pi U_0/\lambda$.
In this section we fix the landscape parameters
to $A_{p} = 0.1\,F_0$ 
with $N_p=20$ minima, 
corresponding to a spatial period $\lambda = 2.3\,a_0$.
The competition between the driving force and the landscape potential
can produce a variety of hopping patterns in the particle motion. 
The relative values of $F_{\rm ac}$, $F_{\rm dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.
If $F_{\rm d}(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
If the driving frequency is low,
as in Fig.~\ref{fig:2_Fd_vy_time},  
the driven particle 
moves 
in a pattern 
with the same frequency 
as the time-dependent force $F_{\rm d}(t)$,
but is modulated by the landscape period.
We explore changes in the frequency and different values of $F_{\rm ac}$ 
in Problem~\ref{ex:parameters}.
Here we vary $F_{\rm dc}$ 
while holding the remaining parameters fixed.

@@

In Fig.~\ref{fig:2_Fd_vy_time}(a)
we plot $F_{\rm d}(t)$ 
as a function of time with the
constants $F_{\rm dc}=0.07$, 
$F_{\rm ac}=0.07$ and $f=0.01$ cycles per time unit $\tau$.
The temporal period of the driving force is
$T = 1/f = 100\,\tau$.
In Fig.~\ref{fig:2_Fd_vy_time}(b) 
we show the $y$-position of the particle
as a function of time,
where we have
normalized $y$ by $\lambda$.
The initial particle position is $y = 0$. 
The particle moves
in the positive $y$-direction
through a distance $\Delta y = \lambda$  in a time $T$,
so that  
the average velocity 
$\langle {v}_y \rangle = \lambda f$. 
The inset of Fig.~\ref{fig:2_Fd_vy_time}(b)
shows $y$ 
over one period $100\,\tau < t < 200\,\tau$
with 
the contour plot described
in Fig.~\ref{fig:1_landscape}(a).
The motion is synchronized such that the 
driving force is a maximum when the landscape 
force is minimum,
as shown by the coincidence of the
steep slope of 
$y/\lambda$ 
and the maxima in $F_{\rm d}(t)$.
When $F_{\rm d}(t)$ is large,
the particle moves across the substrate maxima,
%[DM - color change]
shown in gray with the contour plot.
%DM commented out - too much detail
%The slope of $y/\lambda$ equals zero twice
%during a driving period,
%indicating zero
%forward motion 
%due to a coincidence of the negative
%driving force and motion over the landscape maxima.
%------------------------------------------------------------------------
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig2_Fd_vy_time.pdf}
\caption{(a) The applied driving force $F_{\rm d}(t)$ 
  with parameters $F_{\rm dc} = 0.07$, $F_{\rm ac} = 0.07$ and $f=0.01$.
  (b) 
  The $y$-position of the driven particle
  normalized by the period of the substrate $\lambda$.
  The substrate strength is $A_p=0.1$.
  The inset   shows
  the $y$-position
  through the second period $100\tau<t<200\tau$
 along with the contour plot depicting
  the landscape potential described in Fig.~\ref{fig:1_landscape}(a).
  }
\label{fig:2_Fd_vy_time}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig3_sweep_vyFDC.pdf}
\caption{Average particle velocity  $\langle v_{y} \rangle$
  as a function of $F_{\rm dc}$.
  We let
  $F_{\rm ac}=0.0$ (blue dashed) and 
  $F_{\rm ac}=0.07$ (orange) with $f = 0.01$ 
  as in Fig.~\ref{fig:2_Fd_vy_time}.
  The value of $F_{\rm dc}$ for the first four steps
  %is given,
  correspond with the
  panels (a-d) 
  %indicating a system
  plotted in Fig.~\ref{fig:4_phase}.
  %[DM - clarified?  xx don't understand meaning of indicating a system
  %plotted in Fig.~\ref{fig:4_phase} xx]
}
\label{fig:3_sweep_vyFDC}
\end{figure}

  To study synchronization patterns, 
  it is useful to compare
  mode-locked quantities 
  in a two-dimensional phase plot. 
  For a driven pendulum confined to a single potential well,
  an appropriate
  phase space is the particle velocity $v_y$ versus the position $y$.  
  For a particle driven 
  through multiple identical wells 
  we define phase variables 
  to account for the net increase in the position.
  The phase position is
  \begin{equation}
    \phi(t) = 2\pi [y(t)-\langle v_y \rangle t]/\lambda,
  \end{equation}
  centered about the average particle displacement $\langle v_y \rangle t$
  and normalized by the substrate period $\lambda$.\cite{Juniper2015}
  The phase velocity is
  \begin{equation}
    \dot{\phi}(t) =2\pi [v_y(t)-\langle v_y \rangle] /\lambda.  
  \end{equation}
  For zero landscape force, 
  the phase velocity  is zero when $F_{\rm d}(t) = F_{\rm dc}$.
  %[DM rewrite]
  If the system
  is strictly mode-locked,
  the particle velocity
  recurs at a particular spatial location, and 
  %If the velocity
  %is mode-locked to 
  %a spatial location,
  %[xx don't understand meaning of the velocity
  %is mode-locked to 
  %a spatial location xx]
  a closed loop appears in  
  phase space. 
  A 1:1 mode appears as a circle or oval. 
  Nodes appear 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is nearly phase locked
  will appear as an almost closed loop.
  Such quasiperiodic systems are
  not fully synchronized
  so the position-velocity relation
  shifts in time as in Fig.~\ref{fig:4_phase}.

@@

In the following
we explore the behavior of our model
with suggested problems for interested readers.
We discuss the molecular dynamics algorithm
and
numerical integration techniques in Problem~\ref{ex:euler}.
%DM slight rewrite to remove the redundant ``we'' tense
Changes to the parameters are described in 
%We explore changes in the particle motion
%with parameter changes in
Problem~\ref{ex:parameters}.
We include analytic solutions to  the 
linear drag equation in Problem~\ref{ex:reynolds}, 
the equation of motion in Problem~\ref{ex:n2l}.
%[DM working on it xx see comment below xx]
%DM rewrite of the following sentence - unclear as written/edited
We extend the numerical model %with
%numerical problems 
to include finite temperature effects
in Problem~\ref{ex:brownian}.

\begin{problem}{Write your own MD code}
  \label{ex:euler}

  %[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK. Instead you might want to make this problem 1 and guide readers to write their own program. Then mention that a program is available, which you only mention in the abstract xx]
  To calculate the position of the particle
  %DM add
  as a function of time
  %DM end
  we
  numerically integrate the equation of motion
  %DM add
  (Eq.~\ref{eq:motion})
  %DM end
  using
  the standard definition of velocity
  $\vec{v} = d\vec{r}/dt$ 
  using the 
  Euler method.
  %DM substituted direct reference for ``The equation of motion...''
  Eq.~\ref{eq:motion} provides
  a direct calculation for the particle velocity
  from the net force on the particle,
  as demonstrated in Problem~\ref{ex:n2l}.

@@

   \item[(b)] {\bf Time loop.}
     The Euler method is effective
     for solving linear ordinary differential  equations
     of the form
     $dy/dt = f(t,y(t))$ with the initial condition $y(t_0) = y_0$.
     The solution is calculated algorithmically
     by stepping in time through $n$ integer steps
     $t_n = t_0 + n \Delta t$.
     At each subsequent step the new
     value for $y$ is calculated as a  solution of a map using
     discrete times 
     $y_{n+1} = y_n + f(t_n,y_n)$.
     Apply the Euler method to %our equation of motion
     Eq.~\ref{eq:motion}
     %[DM - resolved xx refer to specific equation by label xx]
     to determine  the analytic expression
     for the position of a particle
     $y_n$ at the $nth$ time step.

@@

  For no applied driving force,
  find 
  the minimum temperature required for a single particle
  to hop over the maxima in the potential landscape.
  Assume the particle is confined to
  move along the $y$-direction,
  include Brownian motion 
  in the model.
  Appropriate temperatures to explore
  are $T/A_p = 3.0, 3.5$, and $4.0$.
  Plot the $y-position$ versus time
  for this particle.
  %----------------------------------------------------
  %  \begin{figure} %[h!]
  %    \centering
  %    \includegraphics[width=\columnwidth]{{fig8_brownian}.pdf}
  %    \caption{
   %     Motion of a particle undergoing Brownian motion
   %     on a washboard potential
   %     energy landscape.
   %     (a) $T/A_p = 3.0$ no hopping occurs.
   %     (b) $T/A_p = 3.5$ one hop occurs and 
   %     (c) $T/A_p = 4.0$ many hops occur.
   %     Note the scale of the $y$-axis differs in each panel
   %     and the time scale is
   %     greater than in Fig.~\ref{fig:2_Fd_vy_time}.
   %     The precise timing of the hop pattern varies,
%sometimes exhibiting several hops for $T/A_p = 3.5$. 
%      }
%      \label{fig:8_brownian}
%    \end{figure}
%  
%  In Fig.~\ref{fig:8_brownian}
%  we show the position versus time of a particle
%  confined to a sinusoidal landscape
%  undergoing Brownian motion.
 % We increase the temperature relative
 % to the amplitude of the landscape
 % troughs until the particle enters a hopping regime.
 % In  Fig.~\ref{fig:8_brownian}(a)
 % the temperature is $T/A_p = 3.0$.
 % The particle executes a 
 % random walk centered at the potential minima $y/\lambda = 10$.
 % We ran many simulations and never observed a hop to another minima
 % within this simulation time.  
 % In  Fig.~\ref{fig:8_brownian}(b)
 % $T/A_p = 3.5$,  hops between
 % potential minima are possible but not probable,
 % a hop occurs from
 % $y/\lambda = 10$ to $9$ at
 % $t \sim 23000 \tau$. 
 % In other simulations with identical parameters,
 % we sometimes observed no hops or two hops between minima,
 % as expected with random fluctuating systems.
 % In  Fig.~\ref{fig:8_brownian}(c)
 % $T/A_p = 4.0$ 
 % we observe many hops.
 % The random thermalized kicks are
 % sufficiently large to make the particle perform
 % what appears to be 
 % a random walk of hops atop the substrate. %[xx what is the question? xx]

>>>>

\section{Introduction} 
Synchronization is a universal phenomena
in which
individual oscillators change frequency due
to external stimuli.\cite{Pikovsky2003}
The
flickering patterns of
candle flames [DM - the air molecules are oscillating xx is a flame an oscillator? xx]
mediated by temperature fluctuations,\cite{Okamoto2016}
the vibrations of singing wine glasses interacting 
through sound waves,\cite{Arane2009}
and metronomes vibrating through a supporting platform\cite{Jia2015}
are examples of in-phase coupled oscillations. 
Biological systems benefit from cooperative
synchronization --
birds coordinate wing flaps
to optimize energy use during flight,\cite{Portugal2014}
frogs alternate croaking patterns,\cite{Aihara2014}
humans clap in time with music,\cite{Tranchant2016}
and 
at a cellular level, 
neurons simultaneously fire in cardiac muscle\cite{MartinHall1999}
and brain tissue.\cite{Singer1999}
External forcing can cause or regulate 
synchronization. For example, 
an electrical pacemaker 
regulates a heart beat 
and 
a pulsed light modifies the
flashing pattern of fireflies.

@@

In Sec.~\ref{sec:conclusion}
we describe how our results apply 
to physical systems,
such as optically trapped colloids
%charge density waves in dusty plasma
[DM rewrote to better align with conclusion xx added words is this correct? xx]
and superconducting vortices in the presence of periodic pinning arrays.
% and Josephson junctions.
[DM resolved xx Josephson junctions not explicitly mentioned in conclusion, xx] 
We include problems for interested readers 
in Sec.~\ref{sec:problems}.

\section{Simulation}
\label{sec:MD}
We use a classical model for 
studying the dynamics, %xx you only use single particles xx]
using the net force on a particle to calculate
its trajectory.
The particle is confined in a two-dimensional (2D) [DM singular]
simulation of area $A = L \times L$, where $L=46.\bar{6}\,a_0$
where $a_0$ is a dimensionless unit of length.
[DM - yes.  in the simulation we just use $L=46.6$ and the $a_0$ is to satisfy readers unfamiliar with simulation units xx confused about the role of $a_0$ because it and hence $L$ are dimensionless, Is it really the size of a colloid particle, which in the simulation you set to unity?  xx]
The particle %Particle $i$
[DM resolved xx since we are doing non-interacting particles and thus only one particle is moving can we eliminate the subscript $i$? xx]
has
position $\vec{r} = x \hat{x} + y \hat{y}$
and velocity $\vec{v} = d\vec{r}/dt$.
The edges of the system are treated by
periodic boundary conditions,
such that a particle leaving the edge of the system is mapped
back to a position within the simulation boundaries 
by the transformation $x+L \rightarrow x$ and $y+L \rightarrow y$.
We show a schematic of the system in Fig.~\ref{fig:1_landscape}(a).
The units of the simulated variables are summarized in Table~\ref{tab:1}.
%\footnote{To learn more about the effects of temperature on this simulation see Problem~\ref{ex:brownian}, where we study $U_0 \sim k_B T$.}

We confine the particles using a position dependent 
potential energy, called a landscape or substrate.
The landscape is modulated in the $y$-direction
by the periodic function 
 \begin{equation}
   U(y) = U_0 \cos{(2 \pi y / \lambda)},
     \label{eq:ysubstrate}
\end{equation}
where $\lambda=L/N_p$, with $N_p$ equal to the number of periods,
and $U_0$ is a parameter
 that sets the depth of the minima
 with simulation units of energy $E_0$. 
 We plot this function in 
 Fig.~\ref{fig:1_landscape}
 for $N_p = 3$.  In Fig.~\ref{fig:1_landscape}(a) we show 
 the $x$-$y$ plane with a contour plot of $U(y)$ 
 to illustrate
 the 2D potential energy landscape;
 the maxima are colored gray and the minima colored white.
 [DM - switch from red/blue to gray/white - xx make sure that all your figures make sense when printed in b/w xx]

The confining force on the particle [DM removed subscripts] $i$
 is given by
 \begin{equation}
 \vec{F}_{\ell}(\vec{r}) = - \vec \nabla U(\vec{r}). [DM removed ^{\ell}]
 \label{eq:dudr}
 \end{equation}
 %[xx what does the superscript $\ell$ mean? xx]
 where $\ell$ denotes the landscape.
 In Fig.~\ref{fig:1_landscape}(b) we plot  
 $U(y)$ to illustrate how the magnitude
 $|\vec{F}_{\ell}|$ is calculated from the particle position $y$.
 [DM - begrudingly changed - My collaborators and I usually use superscripts for these equations to separate the force superscripts from the particle index subscripts.  This is consistent with the textbook I teach from.  xx suggest that you use subscripts instead of superscripts. We can easily make that change in the next iteration of your manuscript. However, you would need to change the figures, e.g., $\vec{F}_{\rm d}$ $F_{\rm dc}$ $F_{\rm ac}$. One of us didn't like superscripts where he was an undergraduate!  xx]

@@

The equation of motion provides a direct calculation of the velocity
of an individual particle at position $\vec{r}$ 
and simulation time $t$.
The   simulation is controlled by a  loop
which runs to a maximum integer time step.
At each time step
we evaluate the net force on each particle as a function of its position
$\vec{r}(t)$
and then integrate
the equation of motion to move particles
to an updated position.
Because the acceleration is zero,
the integration of the equation of motion
is performed via 
the simple first-order Euler method 
\begin{equation}
  \vec{r}(t+\Delta t) = \vec{v}(t) \Delta t + \vec{r}(t)
    \label{eq:euler}
\end{equation}
for a time step $\Delta t = 0.1\,\tau$.
In 
Problem~\ref{ex:euler}
we describe 
the numerical methods for 
solving differential equations.
%------------------------------------------------------------------
\begin{figure} % [h!]
\centering
\includegraphics[width=\columnwidth]{fig1_landscape.pdf}
\caption{
Schematic of the simulation of a single particle
  driven across a washboard potential energy landscape.
  (a) View of the $x$-$y$ plane. 
  The time-dependent applied driving force $\vec{F}_{\rm d}$
  is parallel to the $y$-axis.
  The landscape is shown with
  [DM changed color scheme from red/blue to gray/white for better BW conversion]
  maxima in the potential energy are gray %#red
  and minima are white %.
  A particle is 
  subject to competing forces of the landscape and applied driving force.
  (b) The potential energy function
  along the $y$-axis $U(y)$.  [DM removed $_{\ell}$]
  The particle in (a) is shown at the same $y$-position.
  The slope of $U(y)$ [DM removed $_{\ell}$ use the subscripts with the potential, but will move to superscript xx used subscript here xx]
  is the 
  magnitude of force $\vec{F}_{\ell}$. 
  }
\label{fig:1_landscape}
\end{figure}
%
\section{Mode-locking of a single particle}
% In subsection headings, only the first word is capitalized.
\label{sec:results}
Here we drive 
a single particle 
across the landscape. 
The numerical implementation of the landscape 
is calculated with Eqs.~\eqref{eq:ysubstrate} and \eqref{eq:dudr}  [DM - right, two negative signs, one from the derivative, the other from the definition of force.  I found the ``mistakenly'' dropped minus sign in the depths of january and added it.  xx but you should get a + sign not a minus sign xx] 
\begin{equation}
  \label{eq:force}
  {F_{\ell}}_y(y) = A_{p} \sin{(2 \pi y / \lambda)},
\end{equation}
where the force is scaled by the parameter $A_{p} = 2\pi U_0/\lambda$.
In this section we fix the landscape parameters
to $A_{p} = 0.1\,F_0$ 
with $N_p=20$ minima, 
corresponding to a spatial period $\lambda = 2.3\,a_0$.
The competition between the driving force and the landscape potential
can produce a variety of hopping patterns in the particle motion. 
The relative values of $F_{\rm ac}$, $F_{\rm dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.
If $F_{\rm d}(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
If the driving frequency is low,
as in Fig.~\ref{fig:2_Fd_vy_time},  
the driven particle 
moves 
in a pattern 
with the same frequency 
as the time-dependent force $F_{\rm d}(t)$,
but is modulated by the landscape period.
We explore changes in the frequency and different values of $F_{\rm ac}$ 
in Problem~\ref{ex:parameters}.
Here we vary $F_{\rm dc}$ 
while holding the remaining parameters fixed.

@@

In Fig.~\ref{fig:2_Fd_vy_time}(a)
we plot $F_{\rm d}(t)$ 
as a function of time with the
constants $F_{\rm dc}=0.07$, 
$F_{\rm ac}=0.07$ and $f=0.01$ cycles per time unit $\tau$.
The temporal period of the driving force is
$T = 1/f = 100\,\tau$.
In Fig.~\ref{fig:2_Fd_vy_time}(b) 
we show the $y$-position of the particle
as a function of time,
where we have
normalized $y$ by $\lambda$.
The initial particle position is $y = 0$. 
The particle moves
in the positive $y$-direction
through a distance $\Delta y = \lambda$  in a time $T$,
so that  
the average velocity 
$\langle {v}_y \rangle = \lambda f$. 
The inset of Fig.~\ref{fig:2_Fd_vy_time}(b)
shows $y$ 
over one period $100\,\tau < t < 200\,\tau$
with 
the contour plot described
in Fig.~\ref{fig:1_landscape}(a).
The motion is synchronized such that the 
driving force is a maximum when the landscape 
force is minimum,
as shown by the coincidence of the
steep slope of 
$y/\lambda$ 
and the maxima in $F_{\rm d}(t)$.
When $F_{\rm d}(t)$ is large,
the particle moves across the substrate maxima,
[DM - color change]
shown in gray with the contour plot.
%DM commented out - too much detail
%The slope of $y/\lambda$ equals zero twice
%during a driving period,
%indicating zero
%forward motion 
%due to a coincidence of the negative
%driving force and motion over the landscape maxima.
%------------------------------------------------------------------------
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig2_Fd_vy_time.pdf}
\caption{(a) The applied driving force $F_{\rm d}(t)$ 
  with parameters $F_{\rm dc} = 0.07$, $F_{\rm ac} = 0.07$ and $f=0.01$.
  (b) 
  The $y$-position of the driven particle
  normalized by the period of the substrate $\lambda$.
  The substrate strength is $A_p=0.1$.
  The inset   shows
  the $y$-position
  through the second period $100\tau<t<200\tau$
 along with the contour plot depicting
  the landscape potential described in Fig.~\ref{fig:1_landscape}(a).
  }
\label{fig:2_Fd_vy_time}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig3_sweep_vyFDC.pdf}
\caption{Average particle velocity  $\langle v_{y} \rangle$
  as a function of $F_{\rm dc}$.
  We let
  $F_{\rm ac}=0.0$ (blue dashed) and 
  $F_{\rm ac}=0.07$ (orange) with $f = 0.01$ 
  as in Fig.~\ref{fig:2_Fd_vy_time}.
  The value of $F_{\rm dc}$ for the first four steps
  %is given,
  correspond with the fixed value of $F_{\rm dc}$
  in each of the phase plots
  %indicating a system
  in Fig.~\ref{fig:4_phase}(a-d).
  [DM - clarified?  xx don't understand meaning of indicating a system
  plotted in Fig.~\ref{fig:4_phase} xx]
}
\label{fig:3_sweep_vyFDC}
\end{figure}

  To study synchronization patterns, 
  it is useful to compare
  mode-locked quantities 
  in a two-dimensional phase plot. 
  For a driven pendulum confined to a single potential well,
  an appropriate
  phase space is the particle velocity $v_y$ versus the position $y$.  
  For a particle driven 
  through multiple identical wells 
  we define phase variables 
  to account for the net increase in the position.
  The phase position is
  \begin{equation}
    \phi(t) = 2\pi [y(t)-\langle v_y \rangle t]/\lambda,
  \end{equation}
  centered about the average particle displacement $\langle v_y \rangle t$
  and normalized by the substrate period $\lambda$.\cite{Juniper2015}
  The phase velocity is
  \begin{equation}
    \dot{\phi}(t) =2\pi [v_y(t)-\langle v_y \rangle] /\lambda.  
  \end{equation}
  For zero landscape force, 
  the phase velocity  is zero when $F_{\rm d}(t) = F_{\rm dc}$.
  [DM rewrite following sentence]
  If the system
  is strictly mode-locked,
  the particle velocity
  recurs at a particular spatial location, and 
  %If the velocity
  %is mode-locked to 
  %a spatial location,
  %[xx don't understand meaning of the velocity
  %is mode-locked to 
  %a spatial location xx]
  a closed loop appears in  
  phase space. 
  A 1:1 mode appears as a circle or oval. 
  Nodes appear 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is nearly phase locked
  will appear as an almost closed loop.
  Such quasiperiodic systems are
  not fully synchronized
  so the position-velocity relation
  shifts in time as in Fig.~\ref{fig:4_phase}.

@@

In the following
we explore the behavior of our model
with suggested problems for interested readers.
We discuss the molecular dynamics algorithm
and
numerical integration techniques in Problem~\ref{ex:euler}.
[DM slight rewrite to remove the redundant ``we'' active voice construction]
Changes to the parameters are described in 
%We explore changes in the particle motion
%with parameter changes in
Problem~\ref{ex:parameters}.
We include analytic solutions to  the 
linear drag equation in Problem~\ref{ex:reynolds}, 
the equation of motion in Problem~\ref{ex:n2l}.
%[DM working on it xx see comment below xx]
%DM rewrite of the following sentence - unclear as written/edited
We extend the numerical model %with
%numerical problems 
to include finite temperature effects
in Problem~\ref{ex:brownian}.

\begin{problem}{Write your own MD code}
  \label{ex:euler}
  %[xx you didn't really discuss other integration algorithms, you just mentioned some names That's OK. Instead you might want to make this problem 1 and guide readers to write their own program. Then mention that a program is available, which you only mention in the abstract xx]
  To calculate the position of the particle
  %DM add
  as a function of time
  %DM end
  we
  numerically integrate the equation of motion
  %DM add
  (Eq.~\ref{eq:motion})
  %DM end
  using
  the standard definition of velocity
  $\vec{v} = d\vec{r}/dt$ 
  using the 
  Euler method.
  %DM substituted direct reference for ``The equation of motion...''
  Eq.~\ref{eq:motion} provides
  a direct calculation for the particle velocity
  from the net force on the particle,
  as demonstrated in Problem~\ref{ex:n2l}.

@@

   \item[(b)] {\bf Time loop.}
     The Euler method is effective
     for solving linear ordinary differential  equations
     of the form
     $dy/dt = f(t,y(t))$ with the initial condition $y(t_0) = y_0$.
     The solution is calculated algorithmically
     by stepping in time through $n$ integer steps
     $t_n = t_0 + n \Delta t$.
     At each subsequent step the new
     value for $y$ is calculated as a  solution of a map using
     discrete times 
     $y_{n+1} = y_n + f(t_n,y_n)$.
     Apply the Euler method to %our equation of motion
     Eq.~\ref{eq:motion}
     [DM - resolved xx refer to specific equation by label xx]
     to determine  the analytic expression
     for the position of a particle
     $y_n$ at the $nth$ time step.

@@

  For no applied driving force,
  find 
  the minimum temperature required for a single particle
  to hop over the maxima in the potential landscape.
  Assume the particle is confined to
  move along the $y$-direction,
  include Brownian motion 
  in the model.
  Appropriate temperatures to explore
  are $3.0 < T/A_p = 7.0$.
  %DM moved position out of math mode
  Plot the $y-$ position versus time
  for this particle.
  %----------------------------------------------------
  %  \begin{figure} %[h!]
  %    \centering
  %    \includegraphics[width=\columnwidth]{{fig8_brownian}.pdf}
  %    \caption{
   %     Motion of a particle undergoing Brownian motion
   %     on a washboard potential
   %     energy landscape.
   %     (a) $T/A_p = 3.0$ no hopping occurs.
   %     (b) $T/A_p = 3.5$ one hop occurs and 
   %     (c) $T/A_p = 4.0$ many hops occur.
   %     Note the scale of the $y$-axis differs in each panel
   %     and the time scale is
   %     greater than in Fig.~\ref{fig:2_Fd_vy_time}.
   %     The precise timing of the hop pattern varies,
%sometimes exhibiting several hops for $T/A_p = 3.5$. 
%      }
%      \label{fig:8_brownian}
%    \end{figure}
%  
%  In Fig.~\ref{fig:8_brownian}
%  we show the position versus time of a particle
%  confined to a sinusoidal landscape
%  undergoing Brownian motion.
 % We increase the temperature relative
 % to the amplitude of the landscape
 % troughs until the particle enters a hopping regime.
 % In  Fig.~\ref{fig:8_brownian}(a)
 % the temperature is $T/A_p = 3.0$.
 % The particle executes a 
 % random walk centered at the potential minima $y/\lambda = 10$.
 % We ran many simulations and never observed a hop to another minima
 % within this simulation time.  
 % In  Fig.~\ref{fig:8_brownian}(b)
 % $T/A_p = 3.5$,  hops between
 % potential minima are possible but not probable,
 % a hop occurs from
 % $y/\lambda = 10$ to $9$ at
 % $t \sim 23000 \tau$. 
 % In other simulations with identical parameters,
 % we sometimes observed no hops or two hops between minima,
 % as expected with random fluctuating systems.
 % In  Fig.~\ref{fig:8_brownian}(c)
 % $T/A_p = 4.0$ 
 % we observe many hops.
 % The random thermalized kicks are
 % sufficiently large to make the particle perform
 % what appears to be 
 % a random walk of hops atop the substrate. %[xx what is the question? xx]

  %{\it Comment: }
  For a driven particle,
  we ignore 
  the effects of temperature 
  in these simulations.  
  We note that even for $T/A_p = 6.0$ 
  the hopping rate
  is much less than the
  frequency of the applied drive. %, as
  %can be seen in the time scale in Fig.~\ref{fig:8_brownian},
  % where the average hopping rate is approximately
  % every $4000\tau$,
  % a value much larger than the period of the driving force.  
  At sufficiently high temperatures,
  Brownian motion does affect 
  the formation of mode-locked steps
  and can be observed in experiments.
\end{problem}
